A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes

### 2023-01-31 pilot-publication/manuscript.Rmd
Draft presentation for meeting on 2023-02-01 and estimate composite outcome
Update Global Burden of Disease citation

Trauma, defined as the clinical entity composed of physical injury and
the body's associated response, causes 4.5 millions deaths every year
[@Naghavi2017]. Almost 10% of the global burden of disease is due
to trauma and trauma is the top contributor to the burden of disease in
children and adults aged 10 to 49 years [@Vos2020].

@@

The study flowchart is shown in Figure X and patient sample
characteristics across trial arms are shown in Table
\@ref(tab:sample-characteristics). Overall, the number of females were
`r n.females` (`r p.females`%), the median age was `r median.age`
years (IQR `r iqr.age`), and the median ISS and NISS were `r median.iss`
(IQR `r iqr.iss`) and `median.niss` (IQR `iqr.niss`) respectively. A 
total of `r n.m30d` (`r p.m30d`%) patients had the primary outcome of 
mortality at 30 days after arrival to the emergency department.

>>>>

Trauma, defined as the clinical entity composed of physical injury and
the body's associated response, causes 4.5 millions deaths every year
[@GBD2018]. Almost 10% of the global burden of disease is due
to trauma and trauma is the top contributor to the burden of disease in
children and adults aged 10 to 49 years [@Vos2020].

@@

The study flowchart is shown in Figure X and patient sample
characteristics across trial arms are shown in Table
\@ref(tab:sample-characteristics). Overall, the number of females were
`r n.females` (`r p.females`%), the median age was `r median.age`
years (IQR `r iqr.age`), and the median ISS and NISS were `r median.iss`
(IQR `r iqr.iss`) and `median.niss` (IQR `iqr.niss`) respectively. The 
number of admitted patients was `r n.admitted` (`r p.admitted`%). A 
total of `r n.m30d` (`r p.m30d`%) patients had the primary outcome of 
mortality at 30 days after arrival to the emergency department.
